```{r set_up, echo = FALSE, results = "hide"}
## themes
library(tidyverse)
library(knitr)
library(kableExtra)

methanol_feed <- runif(1, 100, 500) %>% round(0)
conversion <- runif(1, 0.3, 0.7) %>% round(2)
selectivity <- runif(1, 0.3, 0.7) %>% round(2)
yield <- conversion * selectivity %>% round(2)

feed <- data.frame(meth = methanol_feed, 
                   co = methanol_feed, 
                   h2 = 2*methanol_feed, 
                   water = 0, 
                   ethanol = 0, 
                   acetic = 0)

product <- data.frame(meth = methanol_feed*(1-conversion), 
                      co = methanol_feed*(1-conversion), 
                      h2 = 2*methanol_feed*(1-yield), 
                      water = methanol_feed*yield, 
                      ethanol = methanol_feed*yield, 
                      acetic = methanol_feed*(conversion-yield)) %>% 
  round(2)

rxn_table <- rbind(feed, product) %>% t() %>% as.data.frame()
names(rxn_table) <- c("Feed (kmol/hr)", "Product (kmol/hr)")
rownames(rxn_table) <- c("Methanol", "Carbon Dioxide", "Hydrogen Gas", "Water", "Ethanol", "Acetic Acid")


# solution
sol <- c(conversion, selectivity, yield) * 100
# labels
labels <- c("Conversion", "Selectivity", "Yield")

```

Question
========
  The table below represents the results of a reaction to produce ethanol by reacting methanol, carbon dioxide, and hydrogen gas. Not all the methanol is reacted. There is a competing reaction which produces acetic acid. 
  For your information (this is not necesary to solve the problems), the reactions are given below:
  
$$CH_3OH\:+\:CO\:+\:2H_2\:\rightarrow\:C_2H_5OH\:+\:H_2O$$  
$$CH_3OH\:+\:CO\:\rightarrow\:CH_3COOH$$  
  
  Calculate the  
-  $Conversion\:of\:Methanol$,   
-  $Selectivity\:for\:Ethanol$, and   
-  $Yield\:of\:Ethanol$   
  for this reaction.  
  Give your answer as percentages, just entering a number between 0 and 100 into the boxes below .
  
<br>
  
| $Conversion\:(\%)$   | $Selectivity\:(\%)$  |     $Yield\:(\%)$    |
|:--------------------:|:--------------------:|:--------------------:|
| \#\#ANSWER1\#\#%     | \#\#ANSWER2\#\#%     | \#\#ANSWER3\#\#%     |
  


```{r table, echo = FALSE, comment = NA}
rxn_table %>% kable() %>% kable_styling(bootstrap_options = c("striped", "condensed"))
```



  
```{r questionlist, echo = FALSE, results = "asis"}
answerlist(rep("", length(sol)), markup = "markdown")
```

Solution
========
Apply the formulae:
- $conversion\:=\:\frac{reacted\:methanol}{fed\:methanol}$  
- $selectivity\:=\:\frac{ethanol\:produced}{max.\:ethanol\:from\:reacted\:mehanol}$   
- $yield\:=\:\frac{ethanol\:produced}{ethanol\:that\:could\:be\:produced\:from\:all\:methanol\:fed}$  


```{r solutionlist, echo = FALSE, results = "asis"}
answerlist(paste("$", labels," = ", format(sol), "$", "\\%", sep = ""), markup = "markdown")
```

  
Meta-information
================
extype: cloze
exsolution: `r paste(sol, collapse = "|")`
exclozetype: num|num|num
exname: conversion
extol: 2
exextra[numwidth,logical]: TRUE