```{r data generation, echo = FALSE, results = "hide"}
library(tidyverse)
library(glue)

repeat{
  
  feed_flow <- runif(1, 50, 200) %>% round(0)
  octane_feed_pct <- runif(1, 20, 45) %>% round(0)
  heptane_feed_pct <- runif(1, 20, 45) %>% round(0)
  hexane_feed_pct <- 100 - octane_feed_pct - heptane_feed_pct
  hexane_distil_ratio <- runif(1, 70, 95) %>% round(0)
  octane_bottom_pct <- runif(1, 70, 90) %>% round(0)
  
  feed <- data.frame(total_flow = feed_flow, 
                     octane_flow = feed_flow*octane_feed_pct/100,
                     heptane_flow = feed_flow*heptane_feed_pct/100,
                     hexane_flow = feed_flow*hexane_feed_pct/100,
                     octane_pct = octane_feed_pct,
                     heptane_pct = heptane_feed_pct,
                     hexane_pct = hexane_feed_pct)
  distil <- feed
  bottoms <- feed
  
  distil$hexane_flow <- feed$hexane_flow * hexane_distil_ratio / 100
  distil$octane_flow <- 0
  distil$octane_pct <- 0
  bottoms$octane_flow <- feed$octane_flow
  bottoms$octane_pct <- octane_bottom_pct
  bottoms$total_flow <- bottoms$octane_flow / bottoms$octane_pct *100
  distil$total_flow <- feed$total_flow - bottoms$total_flow
  distil$heptane_flow <- distil$total_flow - distil$hexane_flow
  distil$heptane_pct <- distil$heptane_flow / distil$total_flow *100
  distil$hexane_pct <- distil$hexane_flow / distil$total_flow * 100
  
  bottoms$heptane_flow <- feed$heptane_flow - distil$heptane_flow
  bottoms$hexane_flow <- feed$hexane_flow - distil$hexane_flow
  bottoms$heptane_pct <- bottoms$heptane_flow / bottoms$total_flow *100
  bottoms$hexane_pct <- bottoms$hexane_flow / bottoms$total_flow *100
  
  
  bottoms <- bottoms %>% round(2)
  distil <- distil %>% round(2)
  
  names(feed) <- paste("Feed", names(feed), sep = " ")
  names(distil) <- paste("Distil", names(distil), sep = " ")
  names(bottoms) <- paste("Bottoms", names(bottoms), sep = " ")
  
  # Solution
  sol <- c(feed, distil, bottoms) %>% unlist
  sol_string <- glue("${names(sol)} = {sol}$") %>% 
    str_replace_all("_", " ") %>% 
    str_replace_all(" ", "\\\\:")
  
  if((sum(feed < 0) + sum(distil < 0) + sum(bottoms < 0)) == 0){
    break()
  }
}
```


Question
========

A feed stream goes into a distillation column with a feed flow of $`r feed_flow`kg/hr$ and a composition of $`r octane_feed_pct`$ % octane, $`r heptane_feed_pct`$ % heptane, $`r 100-heptane_feed_pct-octane_feed_pct`$ % hexane. The distillate stream from the column carries $`r hexane_distil_ratio`$% of the hexane fed and virtually no octane. The bottoms stream is $`r octane_bottom_pct`$% octane. Fill out the table below




|                           | $Feed\:Stream\;$    |$Distillate\:Stream\;$ | $Bottoms\:Stream\;$ |
|:-------------------------:|-------------------|---------------------|--------------------|
|$Total\:Flow\:(kg/hr)$     | \#\#ANSWER1\#\#   | \#\#ANSWER8\#\#     | \#\#ANSWER15\#\#   |
|$Octane\:Flow\:(kg/hr)$    | \#\#ANSWER2\#\#   | \#\#ANSWER9\#\#     | \#\#ANSWER16\#\#   |
|$Heptane\:Flow\:(kg/hr)$   | \#\#ANSWER3\#\#   | \#\#ANSWER10\#\#    | \#\#ANSWER17\#\#   |
|$Hexane\:Flow\:(kg/hr)$    | \#\#ANSWER4\#\#   | \#\#ANSWER11\#\#    | \#\#ANSWER18\#\#   |
|$Octane\:Percent\:(\%)$    | \#\#ANSWER5\#\#\% | \#\#ANSWER12\#\#\%  | \#\#ANSWER19\#\#\% |
|$Heptane\:Percent\:(\%)$   | \#\#ANSWER6\#\#\% | \#\#ANSWER13\#\#\%  | \#\#ANSWER20\#\#\% |
|$Hexane\:Percent\:(\%)$    | \#\#ANSWER7\#\#\% | \#\#ANSWER14\#\#\%  | \#\#ANSWER21\#\#\% |

```{r questionlist, echo = FALSE, results = "asis"}
answerlist(rep("", length(sol)), markup = "markdown")
```


Solution
========


```{r solutionlist, echo = FALSE, results = "asis"}
answerlist(sol_string, markup = "markdown")
```


Meta-information
================
extype: cloze
exsolution: `r paste(sol, collapse = "|")`
exclozetype: num|num|num|num|num|num|num|num|num|num|num|num|num|num|num|num|num|num|num|num|num
exname: distillation material balance
extol: 1.0
exextra[numwidth,logical]: TRUE