```{r set_up, echo = FALSE, results = "hide"}
# # themes
# library(tidyverse)
# library(ggExtra)
# library(glue)
# library(ggrepel)
# library(png)
# library(grid)

theme_set(theme_minimal())
#theme_update(panel.border = element_rect(colour = "black", fill=NA, size=2))

xa <- seq(0, 1, 0.001)
alpha <- runif(1, 1.5, 4) %>% round(1)
ya <- alpha*xa/(1+xa*(alpha-1))
vle <- data.frame(xa = xa, ya=ya)

feed <- runif(1, 30, 70) %>% round(0) / 100
q <- runif(1, 0.2, 0.6) %>% round(1)
distil <- runif(1, 0.8, 0.95)
q_slope <- -q / (1-q)
q_end_x <- 0
q_end_y <- feed - q_slope*feed
q_end_x <- ifelse(q_end_y > 1, (1-feed)/q_slope + feed, q_end_x)
q_end_y <- ifelse(q_end_y > 1, 1, q_end_y)

a <- q_slope*(alpha-1)
b <- q_slope - alpha - q_slope*alpha*feed + alpha*feed + q_slope*feed - feed
c <- -q_slope*feed + feed
x <- (-b+sqrt(b^2-4*a*c)*c(-1, 1))/2/a
x <- x[x > 0 & x < 1]
y <- alpha*x / (1+x*(alpha-1))
rectifying_slope <- (distil - y) / (distil - x)
rmin_intercept <- distil*(1-rectifying_slope)
rmin <- distil/rmin_intercept - 1

## solution
sol <- c(q, rmin) %>% round(3)
answer_list <- c("liquid fraction, q", "minimum reflux")
```

Question
========
  
  The diagram below shows part of a McCabe-Thiel diagram with the q-line (green) and the rectifying line (blue) for minimum reflux drawn in. Use this diagram to estimate the liquid fraction, $q$, of the feed stream and the minimum reflux ratio, $R_{min}$.
  
|$q$              |    $R_{min}$         |
|:---------------:|:--------------------:|
|\#\#ANSWER1\#\#  | \#\#ANSWER2\#\#     |

```{r plot_output, echo = FALSE, comment = NA, fig.cap = "", fig.align='center', out.width = "80%"}
vle %>% ggplot(aes(xa, ya)) + 
  geom_line() + 
  geom_abline(intercept = 0, slope = 1, col = "red") + 
  labs(title = "Vapour Liquid Equilibrium Diagram",
       x = "Liquid Fraction of Component A - x",
       y = "Vapour Fraction of Component A - y") +
  scale_x_continuous(breaks = seq(0, 1, 0.1), limits = c(0, 1), minor_breaks = seq(0, 1, 0.05)) +
  scale_y_continuous(breaks = seq(0, 1, 0.1), limits = c(0, 1), minor_breaks = seq(0, 1, 0.05)) +
  geom_vline(xintercept = c(0, 1)) + 
  geom_hline(yintercept = c(0, 1)) + 
  geom_segment(aes(x = feed, y = feed, xend = q_end_x, yend = q_end_y), col = "green") + 
  geom_segment(aes(x = 0, y = rmin_intercept, xend = distil, yend = distil), col = "blue")
```



```{r questionlist, echo = FALSE, results = "asis"}
answerlist(rep("", length(sol)), markup = "markdown")
```


Solution
========
  The slope of the q-line is given by: $slope\;=\;\frac{-q}{1-q}$. From the diagram, this slope is about $`r q_slope`$. The intercept of the rectifying line on the y-axis is given by $intercept\;=\;\frac{x_D}{1+R_{min}}$ so $`r rmin_intercept %>% signif(3)` = \frac{`r distil %>% signif(3)`}{1 + R_{min}}$
  


```{r solutionlist, echo = FALSE, results = "asis"}
answerlist(paste("$", answer_list, " = ", sol, "$", sep = ""), markup = "markdown")
```

  
  
Meta-information
================
extype: cloze
exsolution: `r paste(sol, collapse = "|")`
exclozetype: num|num
exname: mccabe
extol: 0.02
exextra[numwidth,logical]: TRUE