```{r set_up, echo = FALSE, results = "hide"}
## themes
# library(tidyverse)
# library(ggExtra)
# library(glue)
# library(ggrepel)
# library(png)
# library(grid)
# library(exams)

theme_set(theme_minimal())
theme_update(panel.grid.minor = element_line(colour = "darkgrey"),
             panel.grid.major = element_line(colour = "darkslategrey"))
#theme_update(panel.border = element_rect(colour = "black", fill=NA, size=2))

xa <- seq(0, 1, 0.001)
alpha <- runif(1, 1.5, 4) %>% round(1)
ya <- alpha*xa/(1+xa*(alpha-1))
vle <- data.frame(xa = xa, ya=ya)

index <- runif(1, 100, 900) %>% round(0)

## solution
yb <- 1 - vle$ya[index]
```

Question
========
  
  The diagram below shows a VLE curve for two components, $A$ and $B$. Use this VLE curve to estimate the fraction of the less volatile component, $B$, in the vapour phase when the fraction of the more volatile component, $A$, in the liquid phase is $`r vle$xa[index] %>% round(2)`$

```{r plot_output, echo = FALSE, comment = NA, fig.cap = "", fig.align='center', fig.width = 6, fig.height=6}
vle %>% ggplot(aes(xa, ya)) + 
  geom_line() + 
  geom_abline(intercept = 0, slope = 1, col = "red") + 
  labs(title = "Vapour Liquid Equilibrium Diagram",
       x = "Liquid Fraction of Component A - x",
       y = "Vapour Fraction of Component A - y") +
  scale_x_continuous(breaks = seq(0, 1, 0.1), limits = c(0, 1), minor_breaks = seq(0, 1, 0.05)) +
  scale_y_continuous(breaks = seq(0, 1, 0.1), limits = c(0, 1), minor_breaks = seq(0, 1, 0.05)) +
  geom_vline(xintercept = c(0, 1)) + 
  geom_hline(yintercept = c(0, 1))
```


Solution
========
  The fraction of the less volatile component, $B$, in the vapour phase is 1- the fraction of $A$ in the vapour phase $=\; 1- `r vle$ya[index] %>% round(2)` = `r yb %>% round(2)`$
  

  
  
  
  Meta-information
================
  extype: num
exsolution: `r fmt(yb)`
exname: alpha
extol: `r 0.05*yb`