```{r set_up, echo = FALSE, results = "hide"}
## themes
library(tidyverse)
library(ggExtra)
library(glue)
library(ggrepel)

habit <- runif(1, 0, 2) %>% round(0)
# 0. Body Centered Cubic
# 1. Face Centered Cubic
# 2. Primitive Cubic

habit <- 1 # FCC
theme_set(theme_minimal())
theme_update(text = element_text(family = "Ink Free", size = 20))

harmon_1 <- rnorm(1, 14, 1)
harmon_2 <- rnorm(1, 11, 1)
harmon_3 <- rnorm(1, 6.5, 0.5)

multiplier <- function(x){
  0.003 +abs(sin(2*x/harmon_1) * sin(2*x/harmon_2) * sin(2*x/harmon_3) / (2*x)) + 1/(30*2*x)
}

za <- expand_grid(z1=0:4, z2=0:4, z3=0:4) %>% 
  filter(z1>=z2, z2>=z3, z1>0)

s <- ifelse(habit == 0 , za <- za %>%  filter((z1 + z2 + z3) %% 2 ==0), 
       ifelse(habit == 1, za <- za %>% filter((z1 %% 2 + z2 %% 2 + z3 %% 2) %in% c(0, 3)),
                     za <- za))

lambda <- 0.154051
lattice <- runif(1, 0.45, 0.7)
two_theta <- seq(10, 60, 0.005)
fcc <- data.frame(h = za$z1, 
                  k = za$z2, 
                  l = za$z3) %>% 
  mutate(h2k2l2 = (h^2+k^2+l^2)) %>% 
  mutate(d = lattice/sqrt(h2k2l2)) %>% 
  mutate(theta = 180/pi * asin(lambda/2/d) + rnorm(1, 0, 0.4),
         hkl = glue("({h} {k} {l})")) %>% 
  mutate(height = multiplier(theta)) %>% 
  filter(theta < 30)

noise <- rnorm(length(two_theta), 0, sd = 0.0002)

spectrum <- data.frame(two_theta = two_theta) %>% 
  mutate(intensity = dnorm(two_theta, mean = 2*fcc$theta, sd = 0.2) * 
                        (0.003+abs(sin(two_theta/harmon_1) * sin(two_theta/harmon_2) * sin(two_theta/harmon_3) / two_theta)) + noise + 1/(30*two_theta))

# solution
sol <- fcc$d[1:3] %>% round(4)
# labels
labels <- fcc$hkl[1:3]

```

Question
========
  Examine the powder X-ray diffraction spectrum below. Estimate the $2\theta$ values for the three labelled peaks and use these to calculate the interplanar separations, d, for each peak. The value for the X-ray wavelength is $\lambda\;=\;`r lambda`nm$.
  


|$(hkl)$        |    $(111)$           |      $(200)$         |     $(220)$          |
|:-------------:|:--------------------:|:--------------------:|:--------------------:|
|$d$            | \#\#ANSWER1\#\#\ nm  | \#\#ANSWER2\#\#\ nm  | \#\#ANSWER3\#\#\ nm  |

  
```{r plot_output, echo = FALSE, comment = NA, fig.width=10}
spectrum %>% ggplot(aes(two_theta, intensity)) + 
  geom_line(colour = "lightblue") + 
  geom_text_repel(data = fcc %>% filter(h2k2l2 < 10), aes(x = 2*theta, y = height+0.0015, label = hkl)) +
  labs(x = "2θ") +
  scale_x_continuous(breaks = seq(15, 55, by = 5), minor_breaks = seq(15, 55, by = 1))
```

  
```{r questionlist, echo = FALSE, results = "asis"}
answerlist(rep("", length(sol)), markup = "markdown")
```

Solution
========
Apply the formula $n\lambda\;=\;2\times d\times sin(\theta)$


```{r solutionlist, echo = FALSE, results = "asis"}
answerlist(paste("$d_{", labels,"} = ", format(sol), "$", "nm", sep = ""), markup = "markdown")
```

  
Meta-information
================
extype: cloze
exsolution: `r paste(sol, collapse = "|")`
exclozetype: num|num|num
exname: xray d values
extol: 0.02
exextra[numwidth,logical]: TRUE